Hypertension and microbiome

### 2020-01-30 articletwo.Rmd
Most recent

```{r temp}
temp <- readRDS("data/phfinrisk_species_all_drop50k_2018-12-21.RDs")
temp %>% meta %>% nrow
```

@@

```{r Characteristics}
characteristicsTable(meta(pseq.species)) %>% kable
```

@@

```{r scatter plot from deseq}
g.salt <- saltboxplot(pseq.genus.salt, dds.salt)
ggsave(file = "cache/gsalt.png", plot = g.salt, height = 3, width = 3, dpi = 300)
```

@@

```{r write supplement}
core.names.fourcols <- pseq.genus.coretaxa %>%
    renametaxa %>%
    sort %>%
    list.partition %>%
    mycbind

pseq.genus.coretaxa %>% length

core.names.flextable <- flextable(core.names.fourcols) %>%
    flextable::fontsize(size = 10, part = "header") %>%
    flextable::fontsize(size = 10, part = "body") %>%
    flextable::width(j=1:4, width = 1.8) %>%
    flextable::align(align = "left", part = "header") %>%
    flextable::align(align = "left")
core.names.flextable
```

@@

```{r supplement table deseq}
deseq.table.na <- dset.deseq.signf.na %>%
    mutate(lfc_se = sprintf("%.2f±%.2f", log2FoldChange, lfcSE),
           p.value = pub.p(qval)) %>%
    myspread %>%
    select(Feature, starts_with("Systolic"), starts_with("Diastolic"), starts_with("Pulse pressure"),
           starts_with("MAP"), starts_with("Hypertension"))

>>>>

@@

```{r Characteristics}
characteristicsTable(meta(pseq.species)) %>% kable
``

@@

```{r scatter plot from deseq}
g.salt <- saltboxplot(pseq.genus.salt, dds.salt)
ggsave(file = "cache/gsalt.png", plot = g.salt, height = 5, width = 5, dpi = 300)
```

@@

```{r write supplement}
core.names.incols <- pseq.genus.coretaxa %>%
    renametaxa %>%
    sort %>%
    list.partition %>%
    mycbind %>%
    as.data.frame

core.names.flextable <- flextable(core.names.incols) %>%
    flextable::fontsize(size = 10, part = "header") %>%
    flextable::fontsize(size = 10, part = "body") %>%
    flextable::width(j=1:3, width = 1.8) %>%
    flextable::align(align = "left", part = "header") %>%
    flextable::align(align = "left")

core.names.flextable %>% save_as_html("cache/s1.html")
```

@@

```{r supplement table deseq na}
deseq.table.na <- dset.deseq.signf.na %>%
    mutate(lfc_se = sprintf("%.2f±%.2f", log2FoldChange, lfcSE),
           p.value = pub.p(qval)) %>%
    myspread %>%
    select(Feature, starts_with("Systolic"), starts_with("Diastolic"), starts_with("Pulse pressure"),
           starts_with("MAP"), starts_with("Hypertension"))
